---
title: "Exp1 Pilot"
output: html_document
date: "2023-03-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library('tidyverse')
library("purrr")
library("uuid")
library('lubridate')
library('ggplot2')

#theme_set(theme_classic())
```

```{r get data}
df.ppt <- read.csv('../../../data/pilot/PROCESSED_DATA/pilot_exp1_ppt.csv')
df.trial <- read.csv('../../../data/pilot/PROCESSED_DATA/pilot_exp1_trial.csv')
```

```{r}
#exclusions go here (or in a separate thing)
```

## Demographics Stats
```{r summarize ppt}

df.ppt %>%
  count(age_years) %>%
  knitr::kable()

df.ppt %>%
  count(gender) %>%
  knitr::kable()

df.ppt %>%
  count(knower_level_cp_subset) %>%
  knitr::kable()
```

```{r}
df.trial <- df.trial %>%
  mutate(correct_count_no_na = ifelse(is.na(correct_count), 0, 1), 
         correct_count_approx_no_na = ifelse(is.na(correct_count_approx), 0, 1)) 
```

## Results
### Correct set chosen
Q: In cases where kids don't overtly count, is it okay to assume they have counted the correct set if they give the correct count? YES? 
```{r}
ggplot(data = df.trial, 
       mapping = aes(x = knower_level_cp_subset, y = correct_set_chosen)) + 
  geom_jitter(aes(color = id), 
              height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
    facet_grid(~ magnitude) + 
  theme(legend.position = "none")

ggplot(data = df.trial, 
       mapping = aes(x = age_years, y = correct_set_chosen)) + 
  geom_jitter(aes(color = id), 
              height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  theme(legend.position = "none")

ggplot(data = df.trial, 
       mapping = aes(x = age_years, y = correct_set_chosen)) + 
  geom_jitter(aes(color = id), 
              height = 0, 
              alpha = 0.5) +  
  geom_bar(aes(fill = as.factor(age_years)),
           stat = "summary", 
           fun.y = "mean") +
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  facet_grid(magnitude ~ knower_level_cp_subset) + 
  theme(legend.position = "none")
```

### Correct count
CP knowers are at ceiling for small sets but not for large sets. 
Subset knowers are average for small sets but at floor for large sets. 
```{r}
ggplot(data = df.trial, 
       mapping = aes(x = knower_level_cp_subset, y = correct_count)) + 
  geom_jitter(aes(color = id), 
              height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  facet_grid(~ magnitude) + 
  theme(legend.position = "none")

ggplot(data = df.trial, 
       mapping = aes(x = age_years, y = correct_count)) + 
  geom_jitter(aes(color = id), 
              height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  theme(legend.position = "none")

ggplot(data = df.trial, 
       mapping = aes(x = age_years, y = correct_count)) + 
  geom_jitter(aes(color = id), 
              height = 0, 
              alpha = 0.5) +  
  geom_bar(aes(fill = as.factor(age_years)),
           stat = "summary", 
           fun.y = "mean") +
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  facet_grid(magnitude ~ knower_level_cp_subset) + 
  theme(legend.position = "none")
```

### Approximate correct count
Rose only did this for large set, but this makes subset knowers perform almost as well as CP knowers
```{r}
ggplot(data = df.trial %>% filter(magnitude == "large"), 
       mapping = aes(x = knower_level_cp_subset, y = correct_count_approx)) + 
  geom_jitter(aes(color = id), 
              height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  facet_grid(~ magnitude) + 
  theme(legend.position = "none")

ggplot(data = df.trial %>% filter(magnitude == "large"), 
       mapping = aes(x = age_years, y = correct_count_approx)) + 
  geom_jitter(aes(color = id), 
              height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  theme(legend.position = "none")

ggplot(data = df.trial %>% filter(magnitude == "large"), 
       mapping = aes(x = age_years, y = correct_count_approx)) + 
  geom_jitter(aes(color = id), 
              height = 0, 
              alpha = 0.5) +  
  geom_bar(aes(fill = as.factor(age_years)),
           stat = "summary", 
           fun.y = "mean") +
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  facet_grid(magnitude ~ knower_level_cp_subset) + 
  theme(legend.position = "none")
```
### Error size
```{r}
ggplot(data = df.trial, 
       mapping = aes(x = knower_level_cp_subset, y = abs(count_error))) + 
  geom_jitter(aes(color = id), 
              height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  facet_grid(~ magnitude) + 
  theme(legend.position = "none")

ggplot(data = df.trial, 
       mapping = aes(x = age_years, y = abs(count_error))) + 
  geom_jitter(aes(color = id), 
              height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  theme(legend.position = "none")

ggplot(data = df.trial, 
       mapping = aes(x = age_years, y = abs(count_error))) + 
  geom_jitter(aes(color = id), 
              height = 0, 
              alpha = 0.5) +  
  geom_bar(aes(fill = as.factor(age_years)),
           stat = "summary", 
           fun.y = "mean") +
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  facet_grid(magnitude ~ knower_level_cp_subset) + 
  theme(legend.position = "none")
```
